An Analysis of Security Vulnerabilities in Container Images for Scientific Data Analysis

### 2021-03-15 paper.tex
Updated DOI
Editor revision

%%%% Commands %%%%
\newcommand{\todo}[1]{\color{red}\textbf{TODO:}#1\color{black}}
\newcommand{\change}[2]{\color{cyan}Changes: #1\color{black}}
\newcommand{\reprozip}[0]{ReproZip\xspace}
\newcommand{\rom}[1]{\lowercase\expandafter{\romannumeral #1\relax}}
\newcommand{\tristan}[1]{\color{red}From Tristan: #1\color{black}}
\definecolor{ao(english)}{rgb}{0.0, 0.5, 0.0}
\newcommand{\revision}[1]{\color{ao(english)}#1\color{black}\xspace}

@@

The data and scripts used in this study are available in the GitHub repository at
\url{https://github.com/big-data-lab-team/container-vulnerabilities-paper}
with a Jupyter notebook to regenerate the figures. This manuscript is based on 
version 0.1 of the repository, available as DOI \href{https://doi.org/10.5281/zenodo.4136599}{10.5281/zenodo.4136599}.

>>>>

%%%% Commands %%%%
\newcommand{\todo}[1]{\color{red}\textbf{TODO:}#1\color{black}}
\newcommand{\change}[2]{\color{cyan}Changes: #1\color{black}}
\newcommand{\reprozip}[0]{ReproZip\xspace}
\newcommand{\rom}[1]{\lowercase\expandafter{\romannumeral #1\relax}}
\newcommand{\tristan}[1]{\color{red}From Tristan: #1\color{black}}
\definecolor{ao(english)}{rgb}{0.0, 0.5, 0.0}
\newcommand{\revision}[1]{#1\xspace} %\color{ao(english)}#1\color{black}\xspace}

@@

The data and scripts used in this study are available on GitHub
with a Jupyter notebook to regenerate the figures:
\begin{enumerate}
\item Project name: container-vulnerabilities-paper
\item Project home page:\\ \url{https://github.com/big-data-lab-team/container-vulnerabilities-paper}
\item Operating system: Platform independent
\item Programming language: Python
\item Other requirements: Jupyter >= 1.0.0, Matplotlib >= 3.3.0, NumPy >= 1.19.1, Pandas >=1.0.5, SciPy >= 1.6.0
\item License: GNU General Public License v3.0
\end{enumerate}

\section{Availability of Supporting Data}

Kaur B; Dugré M; Hanna A; Glatard T: Supporting data for ``An Analysis of
Security Vulnerabilities in Container Images for Scientific Data Analysis"
GigaScience Database. 2021. \url{http://dx.doi.org/10.5524/100880}
